### 2020-04-23 Paper/paper.tex
Slight changes to discussion section
Added histogram to paper and convRegressionTest

We chose one of the 62 pairs of galaxies and pulled the associated data. This set consisted of 1294 grayscale model images in .png format and their associated human scores in a text file. The set was already sorted in descending order by score. However, we realized that this data was heavily skewed towards worse models, with more than half of the models having scores below 0.10. In an effort to combat overfitting on bad model images, we used only the first 600 images, which, while still skewed towards worse models, presented a much more evenly distributed data set.

@@

In our second net, we attempted to utilize the superior image recognition characteristics of a convolutional neural net. As a base, we used the convolutional neural net used on the cat problem in OLA 6. In this net, there are two 2D convolution layers that feed into a pooling layerThe main changes made were to kernel size and the final dense layer. There are two 2D convolution layers use a standard ReLu activation function, which are then followed by pooling and dropout layer. It is the passed into a flattening layer and a single dense layer, still iwth a ReLu activation function, before passing though a final dropout layer and into the final dense layer. THe main changes we made to this architecture from OLA 6 were in terms of kernel size, unit size of the dense and convolution layers, and the setup of the final dense layer.

>>>>

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.75\linewidth]{./Images/distribution.png}}
\caption{Distribution of sample models across a range of human scores from 0-1.}
\label{fig:distribution}
\end{figure}

We chose one of the 62 pairs of galaxies and pulled the associated data. This set consisted of 1294 grayscale model images in .png format and their associated human scores in a text file. The set was already sorted in descending order by score. However, we realized that this data was heavily skewed towards worse models, with more than half of the models having scores below 0.10. In an effort to combat overfitting on bad model images, we used only the first 600 images, which, while still skewed towards worse models (see Fig. \ref{distribution.png}), presented a much more evenly distributed data set.

@@

In our second net, we attempted to utilize the superior image recognition characteristics of a convolutional neural net. As a base, we used the convolutional neural net used on the cat problem in OLA 6. In this net, there are two 2D convolution layers that feed into a pooling layerThe main changes made were to kernel size and the final dense layer. There are two 2D convolution layers use a standard ReLu activation function, which are then followed by pooling and dropout layer. It is the passed into a flattening layer and a single dense layer, still with a ReLu activation function, before passing though a final dropout layer and into the final dense layer. The main changes we made to this architecture from OLA 6 were in terms of kernel size, unit size of the dense and convolution layers, and the setup of the final dense layer.
